Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-05-13 xrb/paper.tex
some tweaks

%\documentclass[12pt, preprint]{aastex}
\documentclass[twocolumn,times,tighten]{aastex62}

@@

\setlength{\marginparwidth}{0.5in}
\newcommand{\MarginPar}[1]{\marginpar{\vskip-\baselineskip\raggedright\tiny\sffamily\hrule\smallskip{\color{red}#1}\par\smallskip\hrule}}

@@

@@

Laterally propagating detonations were modeled by
\citet{fryxellwoosley82,hedet}, but these would only be applicable at
very high densities, since it is difficult to detonation helium at the
densities found in normal XRBs, and even harder to detonation hydrogen
because of the waiting times for weak reactions.  This means that
detonations may only really be applicable to superbursts (where carbon
is the reactant).

@@

Challenges: timescale for flame propagation, lengthscales (flame
width, Rossby scale), reaction network size.\MarginPar{from talk}

@@

All simulations are performed with the \castro\ hydrodynamics
code~(\citealt{castro}; see also \citealt{astronum:2017} for a recent
description).  We evolve the system of fully compressible Euler
equations for reacting flow:
\begin{eqnarray}
\frac{\partial( \rho X_k)}{\partial t} &=& - \nabla\cdot (\rho \Ub X_k) + \rho \omegadot_k \\
%
\frac{\partial (\rho \Ub)}{\partial t} &=& - \nabla\cdot (\rho \Ub \Ub) - \nabla p +
    \rho \gb \nonumber \\
  &&-2 \rho \Omegab\times \Ub - \Omegab \times (\Omegab \times \rb) \\
%
\frac{\partial (\rho E)}{\partial t} &=& - \nabla \cdot (\rho \Ub E + p\Ub) +
    \nabla \cdot \kth \nabla T + \rho \epsdot +\nonumber\\
  && \rho \Ub \cdot \gb - \rho (\Omegab \cdot \rb)(\Omegab \cdot \Ub) + \rho |\Omegab|^2 (\Ub \cdot \rb)
\end{eqnarray}
Here, $\rho$ is the mass density, $\Ub$ is the velocity, and $E$ is
the specific total energy, which is related to the specific internal
energy as $e = E - |\Ub|^2/2$.  Species are described by mass
fractions, $X_k$ (such that $\sum_k X_k = 1$), and creation rates,
$\omegadot$, and are related to the total specific energy generation
rate, $\epsdot$.  The total mass conservation,
\begin{equation}
\frac{\partial \rho}{\partial t} = - \nabla\cdot (\rho \Ub)
\end{equation}
implies $\sum_k \omegadot_k = 0$.  \castro\ uses an unsplit piecewise
parabolic method (PPM) with characteristic tracing for solving the
hydrodynamics.  Reactions are incorporated via Strang splitting,
giving a method that is overall second-order accurate in space and
time.

 An equation of state of the form $p = p(\rho, e,
\{X_k\})$ completes the thermodynamic description of the
system.  Finally, $\kth$ is the thermal conductivity and $T$ is the
temperature.

>>>>

%\documentclass[12pt, preprint]{aastex}
\documentclass[preprint,times,tighten]{aastex62}

@@

\setlength{\marginparwidth}{0.5in}

\newcommand{\MarginPar}[1]{
    \marginpar{\vskip-\baselineskip%
               \raggedright%
               \tiny\sffamily%
               {\color{red}\hrule%
               \smallskip%
               #1\par%
               \smallskip%
               \hrule}}%
}

\newcommand{\AssignTo}[1]{
    \marginpar{\vskip-\baselineskip%
               \raggedright%
               \tiny\sffamily%
               {\color{blue}\hrule%
               \smallskip%
               #1\par%
               \smallskip%
               \hrule}}%
}

@@

\AssignTo{Mike, Alice}

@@

Laterally propagating detonations were modeled by
\citet{fryxellwoosley82,hedet}, but these would only be applicable at
very high densities, since it is difficult to detonation helium at the
densities found in normal XRBs, and even harder to detonation hydrogen
because of the waiting times for weak reactions.  This means that
detonations may only really be applicable to superbursts (where carbon
is the reactant). \MarginPar{ref}

@@

Challenges: timescale for flame propagation, lengthscales (flame
width, Rossby scale), reaction network size.\MarginPar{summarize AstroNum 2018 paper}

@@

All simulations are performed with the \castro\ hydrodynamics
code~(\citealt{castro}; see also \citealt{astronum:2017} for a recent
description).  We evolve the system of fully compressible Euler
equations for reacting flow:
\begin{eqnarray}
\frac{\partial( \rho X_k)}{\partial t} &=& - \nabla\cdot (\rho \Ub X_k) + \rho \omegadot_k \\
%
\frac{\partial (\rho \Ub)}{\partial t} &=& - \nabla\cdot (\rho \Ub \Ub) - \nabla p +
    \rho \gb \nonumber \\
  &&-2 \rho \Omegab\times \Ub - \Omegab \times (\Omegab \times \rb) \\
%
\frac{\partial (\rho E)}{\partial t} &=& - \nabla \cdot (\rho \Ub E + p\Ub) +
    \nabla \cdot \kth \nabla T + \rho \epsdot +\nonumber\\
  && \rho \Ub \cdot \gb - \rho (\Omegab \cdot \rb)(\Omegab \cdot \Ub) + \rho |\Omegab|^2 (\Ub \cdot \rb)
\end{eqnarray}
Here, $\rho$ is the mass density, $\Ub$ is the velocity, and $E$ is
the specific total energy, which is related to the specific internal
energy as $e = E - |\Ub|^2/2$.  Species are described by mass
fractions, $X_k$ (such that $\sum_k X_k = 1$), and creation rates,
$\omegadot$, and are related to the total specific energy generation
rate, $\epsdot$.  The total mass conservation,
\begin{equation}
\frac{\partial \rho}{\partial t} = - \nabla\cdot (\rho \Ub)
\end{equation}
implies $\sum_k \omegadot_k = 0$.  \castro\ uses an unsplit piecewise
parabolic method (PPM) with characteristic tracing for solving the
hydrodynamics~\cite{ppm,millercolella:2002}, generalized to an
arbitrary equation of state~\cite{zingalekatz}.  Reactions are
incorporated via Strang splitting~\cite{strang:1968}, giving a method that is overall
second-order accurate in space and time.

 An equation of state of the form $p = p(\rho, e,
\{X_k\})$ completes the thermodynamic description of the
system.  Finally, $\kth$ is the thermal conductivity and $T$ is the
temperature.  Diffusion is treated explicitly in time.
